Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-03-24 Grassmannian_cells.tex
started writing

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}

\renewcommand{\AA}{\mathbb{A}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}

@@

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective and preinjective respesentations of a generalized Kronecker quiver admit a cell decomposition.  
  We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
\end{abstract}
\maketitle

\section{Introduction}
-something about cluster algebras
-something about categorification and quiver Grassmannians
-something about compatible pairs and combinatorial construction of cluster variables
-statement of our results
-acknowledgements?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Torus Action on Quiver Grassmannians}
\begin{definition}
  universal cover $\tilde Q$
\end{definition}

\begin{lemma}
  how to lift exceptional representations of $Q$ to $\tilde Q$
\end{lemma}

\begin{lemma}
  $d:\tilde Q_0\to\ZZ$ defines a torus action on $Gr^Q_\bfe(X)$ if $d(q,w\rho)-d(q,w)=c_\rho$ for all $w\in W_{\tilde Q_1}$
\end{lemma}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}

>>>>

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\C}{\mathbb{C}}

\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}

@@

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective and preinjective representations of a generalized Kronecker quiver admit a cell decomposition.  
  We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
\end{abstract}
\maketitle

\section{Introduction}
-something about cluster algebras
-something about categorification and quiver Grassmannians
-something about compatible pairs and combinatorial construction of cluster variables
-statement of our results
-something about torus actions and the universal cover
-something about cell decompositions of quiver Grassmannians
-acknowledgements?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Torus Action on Quiver Grassmannians}
\noindent Let $Q$ be an acylic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$. Moreover, let $W_{Q}$ be the free (non-abelian) group generated by $Q_1$.  We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.
\begin{definition}
The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.

We say that a representation $X\in \Rep(Q)$ can be lifted (to $\tilde Q$) if there exists a representation $\tilde X\in\Rep(\tilde Q)$ such that $F_Q\tilde X=X$ where $F_Q:\Rep(\tilde Q)\to\Rep(Q)$ is the natural functor.
\end{definition}
\begin{lemma}
  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to a representation of $\tilde Q$.
\end{lemma}
\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$. Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the one of $Q$. Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,w)$ of $\tilde Q$. This leads the claim. The statement for preinjective representations follows in the same way.
\end{proof}
We choose a map $d:\tilde Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$. In any case, we can consider the decomposition $X_q=\bigoplus_{w\in W_Q} X_{(q,w)}$. We define a torus action on each $X_{(q,w)}$ via $t.x_{(q,w)}=t^{d(q,w)}x_{(q,w)}$ which can be extended linearly to each $X_q$. For a fixed a subspace $U_q$, we can define the subspace $t.U_q$. In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$. Actually, for this the action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$ and every $x\in X_i$. 
\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
If $X\in\Rep(Q)$ can be lifted, $d:\tilde Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,w\alpha)-d(i,w)=c_\alpha$ for all $\alpha:i\to j$ and $w\in W_{Q}$.
\end{lemma}
\begin{proof} Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,w)}:X_{(i,w)}\to X_{(j,w\alpha)}$. Then the condition $X_{\alpha}(t.U_i)\in t.U_j$ translates into ...to be continued.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
\begin{thebibliography}{10}
\bibitem{bgp}
Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
\end{thebibliography}
